Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-06-14 article.rnw
Add another reference regarding how different traits govern responses than effects.
I haven't used the reference Daniel suggested, as that wasn't dealing with
*competitive* effect and response, but with response to environmental change
and effect on ecosystem processes. However, it did direct me to the
reference I used.

While the results could not definitely identify a single best grouping, it was clear that the model-supported groupings differed for the rows and columns.
That is, species that are similar in their response to competition may not be similar in the competitive effects they have on other species, and vice versa.
In hindsight, this should not be overly surprising since it is known that different traits govern species competitive effects than govern their responses \parencite{goldberg1991competitive}. % DBS: I think it would be good to find another reference here. Maybe this one? https://onlinelibrary.wiley.com/doi/10.1111/j.1365-2486.2008.01557.x
Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
Our results recommend more explicit questioning, and even testing, of this assumption when building future species interaction models.
%TODO: Discuss the fact that species were coclassified more in the rows than in the columns?

>>>>

While the results could not definitely identify a single best grouping, it was clear that the model-supported groupings differed for the rows and columns.
That is, species that are similar in their response to competition may not be similar in the competitive effects they have on other species, and vice versa.
In hindsight, this should not be overly surprising since it is known that different traits govern species competitive effects than govern their responses \parencite{goldberg1990components, goldberg1991competitive}.
Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
Our results recommend more explicit questioning, and even testing, of this assumption when building future species interaction models.
%TODO: Discuss the fact that species were coclassified more in the rows than in the columns?
